Fusion of Mass Spectrometry and Raman Spectroscopy Data

### 2024-06-07 dev/dev_paracetamol.Rmd

stat <- StatisticEngine$new(data = main_set)
stat$make_pca_model(Settings_make_pca_model_mdatools(ncomp = 3, alpha = 0.005, gamma = 0.0005))
stat$predict(test_set)
stat$plot_predicted_distances()
```

>>>>

stat <- StatisticEngine$new(data = main_set)
stat$make_model(Settings_make_model_pca_mdatools(ncomp = 3, alpha = 0.005, gamma = 0.0005))
stat$predict(test_set)
stat$plot_predicted_distances()
```
